---
title: "Homework 6"
author: "Xinyi Lin"
date: "11/16/2018"
output: github_document
---

```{r}
library(tidyverse)
library(modelr)
```

# Problem 1

## Import and tidy data

```{r, message=FALSE}
homicide_df = read_csv("./data/homicide-data.csv") %>% 
  mutate(city_state = str_c(city, ", ", state), 
         bin_diposition = ifelse(disposition == "Closed by arrest", 1, 0),
         victim_age = as.numeric(victim_age),
         victim_race = ifelse(victim_race == "White", "white", "non-white"),
         victim_race = relevel(as.factor(victim_race), ref = "white")) %>% 
  #filter(city_state != "Dallas, TX")
  filter(city_state != "Dallas, TX" & city_state != "Phoenix, AZ" & city_state != "Kansas City, MO" & city_state != "Tulsa, AL")

head(homicide_df)
```

## Baltimore, MD

```{r}
glm_Baltimore =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD") %>% 
  glm(bin_diposition ~ victim_age + victim_sex + victim_race, data = .,family = binomial()) 

#exp(cbind(coef(glm_Baltimore), confint(glm_Baltimore))) %>% 
```

```{r}
glm_estimate =
  glm_Baltimore %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate)) %>%
  select(term, log_OR = estimate, OR, p.value) 

exp(confint(glm_Baltimore)) %>% 
  broom::tidy() %>% 
  rename(term = .rownames, conf_low = X2.5.., conf_high = X97.5..) %>% 
  inner_join(glm_estimate) %>% 
  select(term, OR, conf_low, conf_high, everything())
```

So, the odds ratio of solving homicides comparing non-white victims to white victims keeping all other variable fixed is 0.44 and the confidence interval is (0.31, 0.62).

## Each city

```{r, message=FALSE, warning=FALSE}
get_CI = function(model){
  confint(model) %>% 
    exp() %>% 
  #exp(confint(glm_Baltimore)) %>% 
    broom::tidy() %>% 
    rename(term = .rownames, conf_low = X2.5.., conf_high = X97.5..) %>% 
    as.tibble()
}

# test function
get_CI(glm_Baltimore)   

glm_Albuquerque =
  homicide_df %>% 
  filter(city_state == "Albuquerque, NM") %>% 
  glm(bin_diposition ~ victim_age + victim_sex + victim_race, data = .,family = binomial()) 

glm_Albuquerque

get_CI(glm_Albuquerque)
```

```{r, message=FALSE, warning=FALSE}
cities_glm =
  homicide_df %>% 
  group_by(city_state) %>% 
  nest() %>% 
  mutate(models = map(data, ~glm(bin_diposition ~ victim_age + victim_sex + victim_race, data = .x, family = binomial())), 
         parameters = map(models, broom::tidy)) %>% 
  mutate(CI = map(models, get_CI),
         results = map2(CI, parameters, inner_join)) %>% 
  unnest(results) %>% 
  mutate(OR = exp(estimate)) %>%
  filter(term == "victim_racenon-white") %>% 
  select(city_state, OR, conf_low, conf_high)

head(cities_glm)
```

```{r}
cities_glm %>% 
  mutate(city_state = fct_reorder(city_state, desc(OR))) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf_low, ymax = conf_high)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

According to this plot, we can find that the confidence intervals of OR in different cities are very different Besides, most estimates of OR are smaller than 1.0, so comparing to white victims there are less solving homicides when victims are non-white.

# Problem 2

## Import and tidy data

```{r}
birthweight_df =
  read_csv("./data/birthweight.csv") %>% 
  mutate(frace = as.factor(frace)) 

head(birthweight_df)
```

## Propose model

We used stepwise regression to find out a suitable model.

```{r}
fitted_model <- lm(bwt ~ ., data = birthweight_df)
step(fitted_model, direction = 'both')
```

So one of suitable model is `lm(formula = bwt ~ babysex + bhead + blength + delwt + fincome + frace + gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthweight_df)`

```{r}
own_model = lm(formula = bwt ~ babysex + bhead + blength + delwt + fincome + frace + gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthweight_df) 

broom::tidy(own_model)

broom::glance(own_model)
```

According to the p-value and r-square, we can conclude that this model is effective. Now, we show the plot of model residuals against fitted values.

```{r}
birthweight_df %>% 
  add_predictions(own_model) %>% 
  add_residuals(own_model) %>% 
  ggplot(aes(pred, resid)) +
  geom_hex()
```

## Cross validation 

```{r}
cv_df = 
  crossv_mc(birthweight_df, 100) %>% 
  mutate(train = map(train, as_tibble),
         test = map(test, as_tibble))
```

```{r}
cv_df = 
  cv_df %>% 
  mutate(own_mod = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + frace + gaweeks + mheight + mrace + parity + ppwt + smoken, data = .x)),
         compared_mod1 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         compared_mod2 = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + blength*babysex + babysex*bhead + bhead*blength*babysex, data = .x))) %>% 
  mutate(rmse_own = map2_dbl(own_mod, test, ~rmse(model = .x, data = .y)),
         rmse_mod1 = map2_dbl(compared_mod1, test, ~rmse(model = .x, data = .y)),
         rmse_mod2 = map2_dbl(compared_mod2, test, ~rmse(model = .x, data = .y)))
```

Visualization

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
  mutate(model = str_replace(model, "rmse_", ""),
         model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

